The Splashback Radius of Planck-SZ clusters

### 2019-02-13 Paper_v2/Reply_to_referee.txt

> 
> g) I am not sure that figures 15 and 16 are necessary. I found the written
> explanation of the checks on color scatter perfectly adequate and convincing
> without the figures.

Reply: We agree that the figure XX corresponding to the error as a function of
magnitude may not be necessary, but we would like to show the color cut we use
for reproducibility purposes. We hope the referee will be ok with this.

> 
> 2) Throughout the paper, I found that the writing supposed the reader to
> possess a high level of knowledge about the specifics of the splashback radius
> and its detection. It would be good to add some gentle explanations as well as
> smoother transitions between different sections and arguments. I give some
> examples below.
> 
> a) In the abstract, an introductory sentence would help. What has been done so
> far, why move from optical to SZ selection? A comment to this effect would also
> be good in Section 2.1, some readers are probably confused as to the purpose of
> the SZ sample (which is used only to find clusters but not to constrain their
> profiles).

Reply: We have now included sentences to this effect in the abstract, the
introduction as well as just before Section 2.1.

@@

> 
> e) The corner plots in Figures 10-14, whether they remain in the paper or not,
> would benefit from some explanation. These plots are hard to read: which
> parameters are well-constrained, which are not? Which are dominated by priors?
> Are there important degeneracies? What does all of this mean for the inferred
> splashback radii?

Reply: We have now kept only one of the corner plots, and have written the main
takeaways from the plot in the Results section of the text.

> 
> 3) Some results seem incompatible with results in Baxter+17, and (if real)
> those differences should be discussed.

Reply: We have now added a note discussing our results with those in Baxter et
al. 2017.

@@

> 
> f) Figure 8 looks like a low-resolution pixel graphic. Is there a reason not to
> show it as a vector graphic?

Reply: We have now edited this.

> g) Table 6 would be more useful if it showed the Rsp values computed without
> miscentering for comparison.

Reply: We have added the Rsp values computed without miscentering in Table 6, as suggested.

### 2019-02-13 Paper_v2/Reply_to_referee.txt

>
> f) Showing the corner plots in Figures 10 to 14 is laudable in terms of
> absolute completeness of the information presented, but frankly, I am not sure
> they are necessary. In particular, Figures 10-12 are virtually impossible to
> distinguish by eye, and Figures 13-14 are difficult to digest. I had to stare
> at these figures quite hard to derive any meaningful takeaway messages. My
> suggestions would be to omit all of these figures except perhaps one for one of
> the PanStarrs samples. That figure could then even be put into the main body of
> the paper instead of an appendix.

Reply: We agree with the referee's suggestion and have included one of the
corner plots in the main manuscript and the others have been removed from the
appendix. We have also included some messages that we want the reader to take
from these plots in the text describing this figure.

>
> g) I am not sure that figures 15 and 16 are necessary. I found the written
> explanation of the checks on color scatter perfectly adequate and convincing
> without the figures.

Reply: We agree that the figure 15 corresponding to the error as a function of
magnitude may not be necessary, but we would like to show the color cut we use
for reproducibility purposes. We hope the referee will be ok with this.

@@

>
> e) The corner plots in Figures 10-14, whether they remain in the paper or not,
> would benefit from some explanation. These plots are hard to read: which
> parameters are well-constrained, which are not? Which are dominated by priors?
> Are there important degeneracies? What does all of this mean for the inferred
> splashback radii?

Reply: We have now kept only one of the corner plots, and have written the main
takeaways from the plot in the Results section of the text.

>
> 3) Some results seem incompatible with results in Baxter+17, and (if real)
> those differences should be discussed.

{\bf Still to be done?} Should be done in paragraph starting with: This result
seems to be at odds with the findings ....

@@

>
> f) Figure 8 looks like a low-resolution pixel graphic. Is there a reason not to
> show it as a vector graphic?

Reply: We have now edited this.

> g) Table 6 would be more useful if it showed the Rsp values computed without
> miscentering for comparison.

Reply: We have added the values computed without miscentering as suggested

### 2019-02-13 Paper_v2/RSP_paper_new.tex

\textbf{This result seem to be at odds with the findings presented by
\citet{baxter2017halo}, who find no splashback feature in the blue galaxy
population. Our investigations suggest that the splashback feature gets less
prominent as we proceed to look at galaxies which are progressively bluer in
color. Given that \citet{baxter2017halo}, consider the last quartile of the
blue population, it is imaginable that they see no evidence for the splashback
feature in their dataset. The approach used by \citet{baxter2017halo} used to
separate galaxies into red or blue is also fundamentally different from our
approach. While \citet{baxter2017halo} use K-corrected magnitudes from SDSS
relying on the photometric redshifts of galaxies (which could have different
uncertainties for the red and the blue population), we rely on a color cut
which depends upon the redshift of the cluster under consideration.}

>>>>

\textbf{At face value, this result seems to be at odds with the findings
presented by \citet{baxter2017halo}, who find no splashback feature in the blue
galaxy population. Our independent investigations suggest that the splashback
feature gets less prominent as we cross-correlate the galaxy clusters with
galaxies which are progressively bluer in color. In their paper,
\citet{baxter2017halo} considered the last quartile of the blue population.
Therefore, it is conceivable that they see no evidence for the splashback
feature in their dataset in the bluest population of galaxies. We would also
like to note that the approach used by \citet{baxter2017halo} used to separate
galaxies into red and blue populations is also fundamentally different from our
approach. While \citet{baxter2017halo} use K-corrected magnitudes from SDSS
relying on the photometric redshifts of galaxies (which could have different
uncertainties for the red and the blue population), we rely on a color cut
which depends upon the redshift of the cluster under consideration.}
